Minimal trap spaces of Logical models are maximal siphons of their Petri net encoding

### 2022-06-13 cmsb22.tex
Some more answers

By Theorem~\ref{theo:min_ts_2_max_sp}, we can reduce the problem of computing all minimal trap spaces of a Boolean model to the problem of computing all maximal conflict-free siphons of its Petri net encoding. It is noted that there are no existing methods specifically designed for computing maximal conflict-free siphons (even maximal siphons) of a Petri net. The reason might be that researchers mainly focus on minimal siphons~\cite{DBLP:journals/isci/LiuB16}. Hence, we here propose a new method based on Answer Set Programming (ASP)~\cite{DBLP:journals/aicom/GebserKKOSS11} for computing maximal conflict-free siphons of a Petri net. The details of the proposed method shall be given in the next section.

>>>>

By Theorem~\ref{theo:min_ts_2_max_sp}, we can reduce the problem of computing all minimal trap spaces of a Boolean model to the problem of computing all maximal conflict-free siphons of its Petri net encoding.
Note that in the case of stable states, this can be put in regard to the classical relationship between siphons and deadlocks in Petri nets.
It might actually be possible to generalize our result to any 1-safe place-complementary Petri net to define a notion of trap space that might be useful for the analysis of Petri nets, but this is out of the scope of this article.

It is noted that there are no existing methods specifically designed for computing maximal conflict-free siphons (even maximal siphons) of a Petri net. The reason might be that researchers mainly focus on minimal siphons~\cite{DBLP:journals/isci/LiuB16}. Hence, we here propose a new method based on Answer Set Programming (ASP)~\cite{DBLP:journals/aicom/GebserKKOSS11} for computing maximal conflict-free siphons of a Petri net. The details of the proposed method shall be given in the next section.
